paper3

### 2022-07-08 paper3.Rmd
objective function

#### 1. Initialize domain space for range of values

@@

#### 2. Define objective function

@@

```{python}
import xgboost as xgb

# https://notebooks.githubusercontent.com/view/ipynb?browser=chrome&color_mode=auto&commit=daa2504c337a74778632d44834209425cb6d357f&device=unknown&enc_url=68747470733a2f2f7261772e67697468756275736572636f6e74656e742e636f6d2f4d696c6164536861686964692f46726175642d446574656374696f6e2d5847426f6f73742f646161323530346333333761373437373836333264343438333432303934323563623664333537662f5847426f6f73745f46726175645f446574656374696f6e2e6970796e62&logged_in=false&nwo=MiladShahidi%2FFraud-Detection-XGBoost&path=XGBoost_Fraud_Detection.ipynb&platform=android&repository_id=152300978&repository_type=Repository&version=98
def objective(params, X = X_train, y = y_train, X_early_stop = 100, y_early_stop = 100, n_folds = 10):

    # pos_count = y_train.sum()
    # neg_count = len(y_train) - pos_count
    # imbalance_ratio = neg_count / pos_count

    xgb_clf = xgb.Classifier(**params, n_estimators = 2000, n_jobs = 1)

    xgb_fit_params = {'early_stopping_rounds': 50,
                      'eval_metric': ['logloss'],
                      'eval_set': [(X_early_stop, y_early_stop)],
                      'verbose': True
                      }

    # cv_score = np.mean(cross_val_score(xgb_clf, X_train, y_train, cv = n_folds,
    #                            fit_params = xgb_fit_params, n_jobs = -1,
    #                            scoring = scorer))

    cv_score = np.mean(cohen_kappa_score(xgb_clf,
                                         X_train, 
                                         y_train, 
                                         cv = n_folds, 
                                         fit_params = xgb_fit_params, 
                                         n_jobs = -1, 
                                         scoring = scorer)
                       )

    # hypoeropt minimizes the loss, hence the minus sign behind cv_score
    return {'loss': cv_score, 'status': hyperopt.STATUS_OK, 'params': params}

```{python}
# Classifier:
def hyperparameter_tuning(space):
    model = xgb.XGBClassifier(n_estimators = space['n_estimators'], 
                              max_depth = int(space['max_depth']), 
                              gamma = space['gamma'],
                              reg_alpha = int(space['reg_alpha']),
                              min_child_weight = space['min_child_weight'],
                              colsample_bytree=space['colsample_bytree'])

    evaluation = [( x_train, y_train), ( x_test, y_test)]

    model.fit(x_train, y_train,
            eval_set=evaluation, eval_metric="rmse",
            early_stopping_rounds=10,verbose=False)

    pred = model.predict(x_test)
    accuracy = accuracy_score(y_test, pred>0.5)
    print ("SCORE:", accuracy)
    #change the metric if you like
    return {'loss': -accuracy, 'status': STATUS_OK, 'model': model}

@@

#### 3. Optimization algorithm (Tree Parzen Estimator, tpe)

@@

```{python}
def tune_xgb(param_space, X_train, y_train, X_early_stop = 100, y_early_stop = 100, n_iter = 100):    
    # scorer = make_scorer(conditional_recall_score, needs_proba=True)

    # hyperopt.fmin will only pass the parameter values to objective. So we need to
    # create a partial function to bind the rest of the arguments we want to pass to objective
    # obj = partial(objective,
    #               # scorer = scorer,
    #               X = X_train,
    #               y = y_train,
    #               X_early_stop = X_early_stop,
    #               y_early_stop = y_early_stop)

    # A trials object that will store the results of all iterations
    trials = Trials()

    fmin(fn = objective, 
         space = param_space, 
         algo = tpe.suggest, 
         max_evals = n_iter, 
         trials = trials)

    # returns the values of parameters from the best trial
    return trials.best_trial['result']['params']

>>>>

#### 1. Define a search space

@@

#### 2. Define an objective function

@@

```{python}
import xgboost as xgb
from sklearn.metrics import cohen_kappa_score
from hyperopt import fmin, tpe, hp, STATUS_OK, Trials, space_eval

# https://notebooks.githubusercontent.com/view/ipynb?browser=chrome&color_mode=auto&commit=daa2504c337a74778632d44834209425cb6d357f&device=unknown&enc_url=68747470733a2f2f7261772e67697468756275736572636f6e74656e742e636f6d2f4d696c6164536861686964692f46726175642d446574656374696f6e2d5847426f6f73742f646161323530346333333761373437373836333264343438333432303934323563623664333537662f5847426f6f73745f46726175645f446574656374696f6e2e6970796e62&logged_in=false&nwo=MiladShahidi%2FFraud-Detection-XGBoost&path=XGBoost_Fraud_Detection.ipynb&platform=android&repository_id=152300978&repository_type=Repository&version=98
def objective(params, X_train = X_train, y_train = y_train, X_test = X_test, y_test = y_test):

    model = xgb.XGBClassifier(params,
                              eval_metric = "rmse", 
                              n_estimators = 2000)

    model.fit(X_train, y_train)

    y_pred = model.predict(X_test)
    score = np.mean(cohen_kappa_score(y_test, y_pred))

    return {'loss': score, 'status': STATUS_OK}

@@

#### 3. Minimize the objective over the space

@@

```{python}
from hyperopt import fmin, tpe

trials = Trials()
best = fmin(fn = objective,
            space = param_space,
            algo = tpe.suggest, 
            max_evals = 10)

print(best)
```
